Column Comparison

### 2021-03-08 gc_column_comparison_2.Rmd
new plotting with facet_grid

```{r, fig.width=10, fig.height=10, warning=FALSE}
# Overview Plot
p_fames_db1 <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_grid(rows = vars(column_type), cols = vars(standard_ID), scales = "free_y") +
    ggtitle("FAME Standards Overview") +
    #geom_label_repel(aes(vjust =-7, box.padding = 0.5),
                     #show.legend = FALSE,
                     #size = 2,
                     #segment.alpha = 0.5) +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames_db1
```

>>>>

```{r, fig.width=10, fig.height=10, warning=FALSE}
# Overview Plot
p_fames_db1 <- results %>%
  ggplot() +
    aes(x = `Retention Time`, y = `Relative Height`, fill = saturation, key = `Peak Name`, label = `Peak Name`) +
    geom_bar(stat = 'identity', width = 0.1) +
    facet_grid(rows = vars(column_type), cols = vars(standard_ID), scales = "free_y") +
    ggtitle("FAME Standards Overview") +
    theme_bw() +
    scale_fill_npg() +
    theme(legend.position = "bottom")
p_fames_db1
```
